Poker Chips, Earthquakes, and Computation

### 2014-09-26 draft0.tex
adding one more image

\title{Computing with an Angry Poker Player}
\titlerunning{Computing with an Angry Poker Player}

@@

The paper is organized as follows. In Section~\ref{Definitions and Notation}, we formalize the terminology and operations we use to analyze the game. In Section~\ref{Stability of Finite Boards}, we introduce the idea of a potential function defined on boards to prove that all boards with a finite number of starting chips eventually stabilize. We then modify the potential function to work for infinite boards and we explore its consequences in Section~\ref{Acyclicity of Infinite Boards}. In Section~\ref{Order of Redistribution}, we show that the order in which local earthquakes happens does not matter, thus answering a question in the original problem statement. We then shift our approach in Section ADDSECTIONNAME and present results from our simulations of repeated earthquakes. In particular, we look at the starting arrangement where $n$ chips all start on the same square, and we conjecture based on experimental evidence that such arragnements stabilize after $\Theta(n \log n)$ global earthquakes. In Section~\ref{Board Variants: n-Trees}, we consider what happens when alternative board setups are considered. Finally, in Section~\ref{Computing with Chips} we present a model of computation based on the problem set up, and we show how to construct simple Boolean circuits with AND and OR gates. 
\section{Definitions and Notation}
\label{Definitions and Notation}

@@

\section{Time until Stability}

>>>>

\title{Poker Chips, Earthquakes, and Computation}
\titlerunning{Poker Chips, Earthquakes, and Computation}

@@

The paper is organized as follows. In Section~\ref{Definitions and Notation}, we formalize the terminology and operations we use to analyze the game. In Section~\ref{Stability of Finite Boards}, we introduce the idea of a potential function defined on boards to prove that all boards with a finite number of starting chips eventually stabilize. We then modify the potential function to work for infinite boards and we explore its consequences in Section~\ref{Acyclicity of Infinite Boards}. In Section~\ref{Order of Redistribution}, we show that the order in which local earthquakes happens does not matter, thus answering a question in the original problem statement. We then shift our approach in Section~\ref{Time until Stability} and present results from our simulations of repeated earthquakes. In particular, we look at the starting arrangement where $n$ chips all start on the same square, and we conjecture based on experimental evidence that such arragnements stabilize after $\Theta(n \log n)$ global earthquakes. In Section~\ref{Board Variants: n-Trees}, we consider what happens when alternative board setups are considered. Finally, in Section~\ref{Computing with Chips} we present a model of computation based on the problem set up, and show how to construct simple Boolean circuits and prove some impossibility results. 
\section{Definitions and Notation}
\label{Definitions and Notation}

@@

\section{Time until Stability}
\label{Time until Stability}
